Supplementary Material: District-level male medical and traditional circumcision coverage and unmet need in sub-Saharan Africa

### 2023-09-26 paper/model_spec_ppcs_tables.tex
New model specification tables added

%% Model Specification Table 1: Non-VMMC countries %%
\begin{landscape}

@@

  \begin{tabular}{>{\bfseries}p{0.75cm} 
     >{\bfseries}p{3cm} p{1cm} C{1.25cm} 
     C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} 
     C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm}} 

@@

  & & & \multicolumn{12}{c}{\bf TMC Model} \\ 
  \cmidrule(lr){4-15} 
  & & & \multicolumn{6}{c}{\bf Time invariant} & 
      \multicolumn{6}{c}{\bf Time variant} \\ 
  \cmidrule(lr){4-9} 
  \cmidrule(lr){10-15} 
  & {\bf MMC Model} & {\bf Type} & 
      {\bf CRPS} & {\bf MAE} & {\bf RMSE} & 
      {\bf 50\% CI} & {\bf 80\% CI} & {\bf 95\% CI} & 
      {\bf CRPS} & {\bf MAE} & {\bf RMSE} & 
      {\bf 50\% CI} & {\bf 80\% CI} & {\bf 95\% CI} \\ 

@@

AR1 & No cut-off & MC & 220.73 &   0.16 &   0.21 &  60.51 & \bf 78.47 &  88.84 & \bf220.10 &   0.16 &   0.21 & \bf 60.23 &  78.32 &  88.56 \\ 
  &  & MMC & 167.43 &   0.13 &   0.18 &  68.34 &  84.69 &  93.21 & \bf163.95 & \bf  0.13 & \bf  0.18 &  69.40 &  85.11 & \bf 93.99 \\ 
  &  & TMC & 189.20 &   0.14 &   0.19 &  63.74 &  82.30 &  92.02 & \bf185.47 & \bf  0.14 & \bf  0.19 &  64.23 &  82.45 & \bf 92.25 \\ 
  & Paediatric cut-off & MC & 220.70 &   0.16 &   0.21 &  60.48 &  78.37 & \bf 88.89 & 220.11 & \bf  0.16 & \bf  0.21 &  60.37 &  78.18 &  88.77 \\ 
  &  & MMC & 168.45 &   0.13 &   0.18 & \bf 68.13 & \bf 84.40 &  92.89 & 165.81 &   0.13 &   0.18 &  69.12 &  84.71 &  93.64 \\ 
  &  & TMC & 191.07 &   0.14 &   0.19 & \bf 63.41 &  82.01 &  91.85 & 188.56 &   0.14 &   0.19 &  63.60 & \bf 81.81 &  91.98 \\ 
 RW1 & No cut-off & MC & 220.08 &   0.17 &   0.22 &  60.81 & \bf 78.89 & \bf 89.06 & 240.11 &   0.18 &   0.23 & \bf 58.56 &  77.33 &  88.16 \\ 
  &  & MMC & 167.60 &   0.13 &   0.18 &  68.34 &  84.54 &  93.22 & 167.02 &   0.13 &   0.19 &  69.26 &  85.35 & \bf 94.08 \\ 
  &  & TMC & 188.94 &   0.14 &   0.20 &  64.08 &  83.05 &  92.49 & 195.44 &   0.15 &   0.21 &  64.40 &  83.21 & \bf 92.59 \\ 
  & Paediatric cut-off & MC & 220.29 &   0.17 &   0.22 &  60.90 &  78.79 &  89.04 & \bf218.79 & \bf  0.16 & \bf  0.21 &  60.51 &  78.83 &  88.97 \\ 
  &  & MMC & 168.66 &   0.13 &   0.18 & \bf 68.24 & \bf 84.39 &  93.19 & \bf165.65 & \bf  0.13 & \bf  0.18 &  69.42 &  84.80 &  93.83 \\ 
  &  & TMC & 190.81 &   0.14 &   0.20 & \bf 63.77 &  82.58 &  92.13 & \bf187.53 & \bf  0.14 & \bf  0.19 &  64.04 & \bf 82.53 &  92.23 \\ 
 RW2 & No cut-off & MC & 220.19 &   0.16 &   0.21 &  60.55 &  78.14 &  88.69 & 219.09 &   0.16 &   0.21 &  60.45 &  78.49 &  88.68 \\ 
  &  & MMC & 167.84 &   0.13 &   0.18 &  68.34 &  84.51 &  93.20 & \bf164.16 & \bf  0.13 & \bf  0.18 &  69.59 &  85.14 & \bf 94.01 \\ 
  &  & TMC & 188.93 &   0.14 &   0.19 &  63.64 &  82.42 &  91.99 & \bf184.27 & \bf  0.14 & \bf  0.19 &  64.73 &  82.86 & \bf 92.25 \\ 
  & Paediatric cut-off & MC & 221.05 &   0.16 &   0.21 & \bf 60.19 &  78.27 &  88.76 & \bf218.97 & \bf  0.16 & \bf  0.21 &  60.47 & \bf 78.59 & \bf 88.78 \\ 
  &  & MMC & 168.58 &   0.13 &   0.18 & \bf 68.33 & \bf 84.33 &  92.93 & 165.97 &   0.13 &   0.18 &  69.13 &  84.60 &  93.63 \\ 
  &  & TMC & 191.49 &   0.14 &   0.20 & \bf 63.23 & \bf 81.74 &  91.71 & 187.82 &   0.14 &   0.19 &  63.78 &  82.34 &  92.00 \\ 

@@

  \caption{Results of the posterior predictive checking in total 
             male circumcision (MC), medical male circumcision (MMC) and 
             traditional male circumcision (TMC) from fitting the 12 candidate 
             models and taking the median value across all Non-VMMC countries. Combinations include 
             (i) Time invariant or Time variant TMC, 
             (ii) No cut off vs. Paediatric cut-off in MMC, and 
             (iii) Autoregressive order 1 (AR1), Random Walk 1 (RW1) or 
             Random Walk 2 (RW2) temporal prior. 
             For all combinations, the within-sample continuous ranked 
             probability scores (CRPS), mean absolute error (MAE) , 
             root mean squared error (RMSE), and the proportion of empirical 
             observations that fell within the 50\%, 80\%, and 95\% 
             quantiles are shown.} 
  \label{tab::PPC1Non-VMMC} 

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
\end{landscape}

@@

AR1 & No cut-off & MC & 220.73 &   0.16 &   0.21 &  60.51 & \bf 78.47 &  88.84 & \bf220.10 &   0.16 &   0.21 & \bf 60.23 &  78.32 &  88.56 \\ 
  &  & MMC & 167.43 &   0.13 &   0.18 &  68.34 &  84.69 &  93.21 & \bf163.95 & \bf  0.13 & \bf  0.18 &  69.40 &  85.11 & \bf 93.99 \\ 
  &  & TMC & 189.20 &   0.14 &   0.19 &  63.74 &  82.30 &  92.02 & \bf185.47 & \bf  0.14 & \bf  0.19 &  64.23 &  82.45 & \bf 92.25 \\ 
  & Paediatric cut-off & MC & 220.70 &   0.16 &   0.21 &  60.48 &  78.37 & \bf 88.89 & 220.11 & \bf  0.16 & \bf  0.21 &  60.37 &  78.18 &  88.77 \\ 
  &  & MMC & 168.45 &   0.13 &   0.18 & \bf 68.13 & \bf 84.40 &  92.89 & 165.81 &   0.13 &   0.18 &  69.12 &  84.71 &  93.64 \\ 
  &  & TMC & 191.07 &   0.14 &   0.19 & \bf 63.41 &  82.01 &  91.85 & 188.56 &   0.14 &   0.19 &  63.60 & \bf 81.81 &  91.98 \\ 
 RW1 & No cut-off & MC & 220.08 &   0.17 &   0.22 &  60.81 & \bf 78.89 & \bf 89.06 & 240.11 &   0.18 &   0.23 & \bf 58.56 &  77.33 &  88.16 \\ 
  &  & MMC & 167.60 &   0.13 &   0.18 &  68.34 &  84.54 &  93.22 & 167.02 &   0.13 &   0.19 &  69.26 &  85.35 & \bf 94.08 \\ 
  &  & TMC & 188.94 &   0.14 &   0.20 &  64.08 &  83.05 &  92.49 & 195.44 &   0.15 &   0.21 &  64.40 &  83.21 & \bf 92.59 \\ 
  & Paediatric cut-off & MC & 220.29 &   0.17 &   0.22 &  60.90 &  78.79 &  89.04 & \bf218.79 & \bf  0.16 & \bf  0.21 &  60.51 &  78.83 &  88.97 \\ 
  &  & MMC & 168.66 &   0.13 &   0.18 & \bf 68.24 & \bf 84.39 &  93.19 & \bf165.65 & \bf  0.13 & \bf  0.18 &  69.42 &  84.80 &  93.83 \\ 
  &  & TMC & 190.81 &   0.14 &   0.20 & \bf 63.77 &  82.58 &  92.13 & \bf187.53 & \bf  0.14 & \bf  0.19 &  64.04 & \bf 82.53 &  92.23 \\ 
 RW2 & No cut-off & MC & 220.19 &   0.16 &   0.21 &  60.55 &  78.14 &  88.69 & 219.09 &   0.16 &   0.21 &  60.45 &  78.49 &  88.68 \\ 
  &  & MMC & 167.84 &   0.13 &   0.18 &  68.34 &  84.51 &  93.20 & \bf164.16 & \bf  0.13 & \bf  0.18 &  69.59 &  85.14 & \bf 94.01 \\ 
  &  & TMC & 188.93 &   0.14 &   0.19 &  63.64 &  82.42 &  91.99 & \bf184.27 & \bf  0.14 & \bf  0.19 &  64.73 &  82.86 & \bf 92.25 \\ 
  & Paediatric cut-off & MC & 221.05 &   0.16 &   0.21 & \bf 60.19 &  78.27 &  88.76 & \bf218.97 & \bf  0.16 & \bf  0.21 &  60.47 & \bf 78.59 & \bf 88.78 \\ 
  &  & MMC & 168.58 &   0.13 &   0.18 & \bf 68.33 & \bf 84.33 &  92.93 & 165.97 &   0.13 &   0.18 &  69.13 &  84.60 &  93.63 \\ 
  &  & TMC & 191.49 &   0.14 &   0.20 & \bf 63.23 & \bf 81.74 &  91.71 & 187.82 &   0.14 &   0.19 &  63.78 &  82.34 &  92.00 \\ 

@@

  \caption{Results of the posterior predictive checking in total 
             male circumcision (MC), medical male circumcision (MMC) and 
             traditional male circumcision (TMC) from fitting the 12 candidate 
             models and taking the median value across all Non-VMMC countries. Combinations include 
             (i) Time invariant or Time variant TMC, 
             (ii) No cut off vs. Paediatric cut-off in MMC, and 
             (iii) Autoregressive order 1 (AR1), Random Walk 1 (RW1) or 
             Random Walk 2 (RW2) temporal prior. 
             For all combinations, the within-sample continuous ranked 
             probability scores (CRPS), mean absolute error (MAE) , 
             root mean squared error (RMSE), and the proportion of empirical 
             observations that fell within the 50\%, 80\%, and 95\% 
             quantiles are shown.} 
  \label{tab::PPC1Non-VMMC} 

@@

>>>>

@@

  \begin{tabular}{>{\bfseries}p{0.05cm} p{0.85cm} p{0.75cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm}} 

@@

  & & & \multicolumn{2}{c}{\bf CRPS} & \multicolumn{2}{c}{\bf MAE} & \multicolumn{2}{c}{\bf RMSE} & \multicolumn{2}{c}{\bf 50\% CI} & \multicolumn{2}{c}{\bf 80\% CI} & \multicolumn{2}{c}{\bf 95\% CI}  \\ 
  \cmidrule(lr){4-5} 
  \cmidrule(lr){6-7} 
  \cmidrule(lr){8-9} 
  \cmidrule(lr){10-11} 
  \cmidrule(lr){12-13} 
  \cmidrule(lr){14-15} 
  & & & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV} & {\bf TI} & {\bf TV}\\ 

@@

    \multicolumn{8}{l}{\textbf{ AR1 }} \\ 
 & \bf MC & \bf NC &  75.81 &  79.00 &   0.11 &   0.11 &   0.14 & \bf  0.13 &  69.56 & \bf 67.22 & \bf 79.51 &  76.71 &  88.42 &  83.81 & \\ 
  &  & \bf PC &  74.99 & \bf 74.65 &   0.11 & \bf  0.11 &   0.14 &   0.14 &  70.30 &  68.93 &  80.58 &  80.55 & \bf 88.84 &  88.60 & \\[3pt] 
  & \bf MMC & \bf NC & \bf123.68 & 133.31 & \bf  0.21 &   0.24 & \bf  0.26 &   0.30 & \bf 50.23 &  59.02 &  71.77 & \bf 78.35 &  85.45 & \bf 89.95 & \\ 
  &  & \bf PC & 132.86 & 127.44 &   0.23 &   0.21 &   0.28 &   0.26 &  46.35 &  45.78 &  67.48 &  66.67 &  81.95 &  80.84 & \\[3pt] 
  & \bf TMC & \bf NC & \bf112.09 & 119.62 & \bf  0.20 &   0.22 & \bf  0.25 &   0.28 &  52.20 &  61.76 &  72.50 & \bf 80.30 &  85.49 & \bf 91.37 & \\ 
  &  & \bf PC & 118.05 & 115.27 &   0.21 &   0.20 &   0.27 &   0.25 & \bf 48.84 &  47.16 &  68.48 &  67.66 &  82.26 &  81.16 & \\[3pt] 
    \multicolumn{8}{l}{\textbf{ RW1 }} \\ 
 & \bf MC & \bf NC &  77.22 &  77.86 &   0.12 &   0.12 &   0.14 &   0.14 &  68.59 & \bf 66.54 &  78.83 &  75.30 &  87.28 &  82.52 & \\ 
  &  & \bf PC &  76.06 & \bf 75.66 &   0.12 & \bf  0.11 &   0.14 & \bf  0.14 &  69.44 &  68.76 &  79.79 & \bf 79.83 & \bf 88.14 &  87.33 & \\[3pt] 
  & \bf MMC & \bf NC & 124.16 & \bf120.06 &   0.21 &   0.22 &   0.27 &   0.28 & \bf 49.28 &  58.79 &  69.78 & \bf 79.64 &  84.24 & \bf 90.66 & \\ 
  &  & \bf PC & 128.45 & 127.44 &   0.22 & \bf  0.21 &   0.27 & \bf  0.26 &  46.65 &  46.26 &  66.77 &  67.68 &  80.68 &  80.87 & \\[3pt] 
  & \bf TMC & \bf NC & 112.48 & \bf106.09 &   0.20 &   0.21 &   0.26 &   0.27 & \bf 51.56 &  61.07 &  71.27 & \bf 81.80 &  85.06 & \bf 92.17 & \\ 
  &  & \bf PC & 115.99 & 114.87 &   0.20 & \bf  0.20 &   0.26 & \bf  0.25 &  48.24 &  47.82 &  67.33 &  68.31 &  81.56 &  81.59 & \\[3pt] 
    \multicolumn{8}{l}{\textbf{ RW2 }} \\ 
 & \bf MC & \bf NC &  77.22 & \bf 53.68 &   0.12 & \bf  0.11 &   0.15 & \bf  0.13 &  68.77 & \bf 68.00 & \bf 79.77 &  78.64 &  88.08 &  86.79 & \\ 
  &  & \bf PC &  74.80 &  74.41 &   0.11 &   0.11 &   0.14 &   0.14 &  70.68 &  69.77 &  81.56 &  80.99 & \bf 90.31 &  89.70 & \\[3pt] 
  & \bf MMC & \bf NC & 124.69 & \bf 96.50 &   0.22 & \bf  0.19 &   0.27 & \bf  0.24 & \bf 48.90 &  52.66 &  69.03 & \bf 76.51 &  83.23 & \bf 89.90 & \\ 
  &  & \bf PC & 128.19 & 126.95 &   0.21 &   0.21 &   0.26 &   0.26 &  46.48 &  46.22 &  66.46 &  66.78 &  80.77 &  80.57 & \\[3pt] 
  & \bf TMC & \bf NC & 112.85 & \bf 89.62 &   0.20 & \bf  0.18 &   0.26 & \bf  0.23 & \bf 50.95 &  55.51 &  70.36 & \bf 78.36 &  83.36 & \bf 90.72 & \\ 
  &  & \bf PC & 115.88 & 115.32 &   0.20 &   0.20 &   0.25 &   0.25 &  48.08 &  47.41 &  67.29 &  67.46 &  80.84 &  81.06 & \\[3pt] 

@@

  \caption{Results of the posterior predictive checking in total male 
    circumcision (MC), medical male circumcision (MMC) and traditional male 
    circumcision (TMC) from fitting the 12 candidate models in Non-VMMCcountries. Combinations include (i) Time invariant (TI) or Time variant (TV) TMC, 
    (ii) No cut off (NC) vs. Paediatric cut-off (PC) in MMC, and (iii) 
    Autoregressive order 1 (AR1), Random Walk 1 (RW1) or Random Walk 2 (RW2) 
    temporal prior. For all combinations, the within-sample continuous ranked 
    probability scores (CRPS), mean absolute error (MAE), root mean square 
    error (RMSE), and the proportion of empirical observations that fell within 
    the 50\%, 80\%, and 95\% quantiles are shown.} 
  \label{tab::PPC2Non-VMMC} 

@@

% \begin{landscape}
% 
% {\linespread{1} 
%   \begin{table}[H] 
%   \centering 
%   \footnotesize 
%   \begin{tabular}{>{\bfseries}p{0.75cm} 
%      >{\bfseries}p{3cm} p{1cm} C{1.25cm} 
%      C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} 
%      C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm}} 
%   \hline  
%   & & & \multicolumn{12}{c}{\bf TMC Model} \\ 
%   \cmidrule(lr){4-15} 
%   & & & \multicolumn{6}{c}{\bf Time invariant} & 
%       \multicolumn{6}{c}{\bf Time variant} \\ 
%   \cmidrule(lr){4-9} 
%   \cmidrule(lr){10-15} 
%   & {\bf MMC Model} & {\bf Type} & 
%       {\bf CRPS} & {\bf MAE} & {\bf RMSE} & 
%       {\bf 50\% CI} & {\bf 80\% CI} & {\bf 95\% CI} & 
%       {\bf CRPS} & {\bf MAE} & {\bf RMSE} & 
%       {\bf 50\% CI} & {\bf 80\% CI} & {\bf 95\% CI} \\ 
%   \hline 
% AR1 & No cut-off & MC & 220.73 &   0.16 &   0.21 &  60.51 & \bf 78.47 &  88.84 & \bf220.10 &   0.16 &   0.21 & \bf 60.23 &  78.32 &  88.56 \\ 
%   &  & MMC & 167.43 &   0.13 &   0.18 &  68.34 &  84.69 &  93.21 & \bf163.95 & \bf  0.13 & \bf  0.18 &  69.40 &  85.11 & \bf 93.99 \\ 
%   &  & TMC & 189.20 &   0.14 &   0.19 &  63.74 &  82.30 &  92.02 & \bf185.47 & \bf  0.14 & \bf  0.19 &  64.23 &  82.45 & \bf 92.25 \\ 
%   & Paediatric cut-off & MC & 220.70 &   0.16 &   0.21 &  60.48 &  78.37 & \bf 88.89 & 220.11 & \bf  0.16 & \bf  0.21 &  60.37 &  78.18 &  88.77 \\ 
%   &  & MMC & 168.45 &   0.13 &   0.18 & \bf 68.13 & \bf 84.40 &  92.89 & 165.81 &   0.13 &   0.18 &  69.12 &  84.71 &  93.64 \\ 
%   &  & TMC & 191.07 &   0.14 &   0.19 & \bf 63.41 &  82.01 &  91.85 & 188.56 &   0.14 &   0.19 &  63.60 & \bf 81.81 &  91.98 \\ 
%  RW1 & No cut-off & MC & 220.08 &   0.17 &   0.22 &  60.81 & \bf 78.89 & \bf 89.06 & 240.11 &   0.18 &   0.23 & \bf 58.56 &  77.33 &  88.16 \\ 
%   &  & MMC & 167.60 &   0.13 &   0.18 &  68.34 &  84.54 &  93.22 & 167.02 &   0.13 &   0.19 &  69.26 &  85.35 & \bf 94.08 \\ 
%   &  & TMC & 188.94 &   0.14 &   0.20 &  64.08 &  83.05 &  92.49 & 195.44 &   0.15 &   0.21 &  64.40 &  83.21 & \bf 92.59 \\ 
%   & Paediatric cut-off & MC & 220.29 &   0.17 &   0.22 &  60.90 &  78.79 &  89.04 & \bf218.79 & \bf  0.16 & \bf  0.21 &  60.51 &  78.83 &  88.97 \\ 
%   &  & MMC & 168.66 &   0.13 &   0.18 & \bf 68.24 & \bf 84.39 &  93.19 & \bf165.65 & \bf  0.13 & \bf  0.18 &  69.42 &  84.80 &  93.83 \\ 
%   &  & TMC & 190.81 &   0.14 &   0.20 & \bf 63.77 &  82.58 &  92.13 & \bf187.53 & \bf  0.14 & \bf  0.19 &  64.04 & \bf 82.53 &  92.23 \\ 
%  RW2 & No cut-off & MC & 220.19 &   0.16 &   0.21 &  60.55 &  78.14 &  88.69 & 219.09 &   0.16 &   0.21 &  60.45 &  78.49 &  88.68 \\ 
%   &  & MMC & 167.84 &   0.13 &   0.18 &  68.34 &  84.51 &  93.20 & \bf164.16 & \bf  0.13 & \bf  0.18 &  69.59 &  85.14 & \bf 94.01 \\ 
%   &  & TMC & 188.93 &   0.14 &   0.19 &  63.64 &  82.42 &  91.99 & \bf184.27 & \bf  0.14 & \bf  0.19 &  64.73 &  82.86 & \bf 92.25 \\ 
%   & Paediatric cut-off & MC & 221.05 &   0.16 &   0.21 & \bf 60.19 &  78.27 &  88.76 & \bf218.97 & \bf  0.16 & \bf  0.21 &  60.47 & \bf 78.59 & \bf 88.78 \\ 
%   &  & MMC & 168.58 &   0.13 &   0.18 & \bf 68.33 & \bf 84.33 &  92.93 & 165.97 &   0.13 &   0.18 &  69.13 &  84.60 &  93.63 \\ 
%   &  & TMC & 191.49 &   0.14 &   0.20 & \bf 63.23 & \bf 81.74 &  91.71 & 187.82 &   0.14 &   0.19 &  63.78 &  82.34 &  92.00 \\ 
%   \hline 
%   \end{tabular} 
%   \caption{Results of the posterior predictive checking in total 
%              male circumcision (MC), medical male circumcision (MMC) and 
%              traditional male circumcision (TMC) from fitting the 12 candidate 
%              models and taking the median value across all Non-VMMC countries. Combinations include 
%              (i) Time invariant or Time variant TMC, 
%              (ii) No cut off vs. Paediatric cut-off in MMC, and 
%              (iii) Autoregressive order 1 (AR1), Random Walk 1 (RW1) or 
%              Random Walk 2 (RW2) temporal prior. 
%              For all combinations, the within-sample continuous ranked 
%              probability scores (CRPS), mean absolute error (MAE) , 
%              root mean squared error (RMSE), and the proportion of empirical 
%              observations that fell within the 50\%, 80\%, and 95\% 
%              quantiles are shown.} 
%   \label{tab::PPC1Non-VMMC} 
% \end{table}} 
% 
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
% \end{landscape}

@@

    \multicolumn{8}{l}{\textbf{ AR1 }} \\ 
 & \bf MC & \bf NC & 220.73 & \bf220.10 &   0.16 &   0.16 &   0.21 &   0.21 &  60.51 & \bf 60.23 & \bf 78.47 &  78.32 &  88.84 &  88.56 & \\ 
  &  & \bf PC & 220.70 & 220.11 &   0.16 & \bf  0.16 &   0.21 & \bf  0.21 &  60.48 &  60.37 &  78.37 &  78.18 & \bf 88.89 &  88.77 & \\[3pt] 
  & \bf MMC & \bf NC & 167.43 & \bf163.95 &   0.13 & \bf  0.13 &   0.18 & \bf  0.18 &  68.34 &  69.40 &  84.69 &  85.11 &  93.21 & \bf 93.99 & \\ 
  &  & \bf PC & 168.45 & 165.81 &   0.13 &   0.13 &   0.18 &   0.18 & \bf 68.13 &  69.12 & \bf 84.40 &  84.71 &  92.89 &  93.64 & \\[3pt] 
  & \bf TMC & \bf NC & 189.20 & \bf185.47 &   0.14 & \bf  0.14 &   0.19 & \bf  0.19 &  63.74 &  64.23 &  82.30 &  82.45 &  92.02 & \bf 92.25 & \\ 
  &  & \bf PC & 191.07 & 188.56 &   0.14 &   0.14 &   0.19 &   0.19 & \bf 63.41 &  63.60 &  82.01 & \bf 81.81 &  91.85 &  91.98 & \\[3pt] 
    \multicolumn{8}{l}{\textbf{ RW1 }} \\ 
 & \bf MC & \bf NC & 220.08 & 240.11 &   0.17 &   0.18 &   0.22 &   0.23 &  60.81 & \bf 58.56 & \bf 78.89 &  77.33 & \bf 89.06 &  88.16 & \\ 
  &  & \bf PC & 220.29 & \bf218.79 &   0.17 & \bf  0.16 &   0.22 & \bf  0.21 &  60.90 &  60.51 &  78.79 &  78.83 &  89.04 &  88.97 & \\[3pt] 
  & \bf MMC & \bf NC & 167.60 & 167.02 &   0.13 &   0.13 &   0.18 &   0.19 &  68.34 &  69.26 &  84.54 &  85.35 &  93.22 & \bf 94.08 & \\ 
  &  & \bf PC & 168.66 & \bf165.65 &   0.13 & \bf  0.13 &   0.18 & \bf  0.18 & \bf 68.24 &  69.42 & \bf 84.39 &  84.80 &  93.19 &  93.83 & \\[3pt] 
  & \bf TMC & \bf NC & 188.94 & 195.44 &   0.14 &   0.15 &   0.20 &   0.21 &  64.08 &  64.40 &  83.05 &  83.21 &  92.49 & \bf 92.59 & \\ 
  &  & \bf PC & 190.81 & \bf187.53 &   0.14 & \bf  0.14 &   0.20 & \bf  0.19 & \bf 63.77 &  64.04 &  82.58 & \bf 82.53 &  92.13 &  92.23 & \\[3pt] 
    \multicolumn{8}{l}{\textbf{ RW2 }} \\ 
 & \bf MC & \bf NC & 220.19 & 219.09 &   0.16 &   0.16 &   0.21 &   0.21 &  60.55 &  60.45 &  78.14 &  78.49 &  88.69 &  88.68 & \\ 
  &  & \bf PC & 221.05 & \bf218.97 &   0.16 & \bf  0.16 &   0.21 & \bf  0.21 & \bf 60.19 &  60.47 &  78.27 & \bf 78.59 &  88.76 & \bf 88.78 & \\[3pt] 
  & \bf MMC & \bf NC & 167.84 & \bf164.16 &   0.13 & \bf  0.13 &   0.18 & \bf  0.18 &  68.34 &  69.59 &  84.51 &  85.14 &  93.20 & \bf 94.01 & \\ 
  &  & \bf PC & 168.58 & 165.97 &   0.13 &   0.13 &   0.18 &   0.18 & \bf 68.33 &  69.13 & \bf 84.33 &  84.60 &  92.93 &  93.63 & \\[3pt] 
  & \bf TMC & \bf NC & 188.93 & \bf184.27 &   0.14 & \bf  0.14 &   0.19 & \bf  0.19 &  63.64 &  64.73 &  82.42 &  82.86 &  91.99 & \bf 92.25 & \\ 
  &  & \bf PC & 191.49 & 187.82 &   0.14 &   0.14 &   0.20 &   0.19 & \bf 63.23 &  63.78 & \bf 81.74 &  82.34 &  91.71 &  92.00 & \\[3pt] 

@@

  \caption{Results of the posterior predictive checking in total male 
    circumcision (MC), medical male circumcision (MMC) and traditional male 
    circumcision (TMC) from fitting the 12 candidate models in VMMCcountries. Combinations include (i) Time invariant (TI) or Time variant (TV) TMC, 
    (ii) No cut off (NC) vs. Paediatric cut-off (PC) in MMC, and (iii) 
    Autoregressive order 1 (AR1), Random Walk 1 (RW1) or Random Walk 2 (RW2) 
    temporal prior. For all combinations, the within-sample continuous ranked 
    probability scores (CRPS), mean absolute error (MAE), root mean square 
    error (RMSE), and the proportion of empirical observations that fell within 
    the 50\%, 80\%, and 95\% quantiles are shown.} 
  \label{tab::PPC1VMMC} 

@@

% \begin{landscape}
% 
% {\linespread{1} 
%   \begin{table}[H] 
%   \centering 
%   \footnotesize 
%   \begin{tabular}{>{\bfseries}p{0.75cm} 
%      >{\bfseries}p{3cm} p{1cm} C{1.25cm} 
%      C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm} 
%      C{1.25cm} C{1.25cm} C{1.25cm} C{1.25cm}} 
%   \hline  
%   & & & \multicolumn{12}{c}{\bf TMC Model} \\ 
%   \cmidrule(lr){4-15} 
%   & & & \multicolumn{6}{c}{\bf Time invariant} & 
%       \multicolumn{6}{c}{\bf Time variant} \\ 
%   \cmidrule(lr){4-9} 
%   \cmidrule(lr){10-15} 
%   & {\bf MMC Model} & {\bf Type} & 
%       {\bf CRPS} & {\bf MAE} & {\bf RMSE} & 
%       {\bf 50\% CI} & {\bf 80\% CI} & {\bf 95\% CI} & 
%       {\bf CRPS} & {\bf MAE} & {\bf RMSE} & 
%       {\bf 50\% CI} & {\bf 80\% CI} & {\bf 95\% CI} \\ 
%   \hline 
% AR1 & No cut-off & MC & 220.73 &   0.16 &   0.21 &  60.51 & \bf 78.47 &  88.84 & \bf220.10 &   0.16 &   0.21 & \bf 60.23 &  78.32 &  88.56 \\ 
%   &  & MMC & 167.43 &   0.13 &   0.18 &  68.34 &  84.69 &  93.21 & \bf163.95 & \bf  0.13 & \bf  0.18 &  69.40 &  85.11 & \bf 93.99 \\ 
%   &  & TMC & 189.20 &   0.14 &   0.19 &  63.74 &  82.30 &  92.02 & \bf185.47 & \bf  0.14 & \bf  0.19 &  64.23 &  82.45 & \bf 92.25 \\ 
%   & Paediatric cut-off & MC & 220.70 &   0.16 &   0.21 &  60.48 &  78.37 & \bf 88.89 & 220.11 & \bf  0.16 & \bf  0.21 &  60.37 &  78.18 &  88.77 \\ 
%   &  & MMC & 168.45 &   0.13 &   0.18 & \bf 68.13 & \bf 84.40 &  92.89 & 165.81 &   0.13 &   0.18 &  69.12 &  84.71 &  93.64 \\ 
%   &  & TMC & 191.07 &   0.14 &   0.19 & \bf 63.41 &  82.01 &  91.85 & 188.56 &   0.14 &   0.19 &  63.60 & \bf 81.81 &  91.98 \\ 
%  RW1 & No cut-off & MC & 220.08 &   0.17 &   0.22 &  60.81 & \bf 78.89 & \bf 89.06 & 240.11 &   0.18 &   0.23 & \bf 58.56 &  77.33 &  88.16 \\ 
%   &  & MMC & 167.60 &   0.13 &   0.18 &  68.34 &  84.54 &  93.22 & 167.02 &   0.13 &   0.19 &  69.26 &  85.35 & \bf 94.08 \\ 
%   &  & TMC & 188.94 &   0.14 &   0.20 &  64.08 &  83.05 &  92.49 & 195.44 &   0.15 &   0.21 &  64.40 &  83.21 & \bf 92.59 \\ 
%   & Paediatric cut-off & MC & 220.29 &   0.17 &   0.22 &  60.90 &  78.79 &  89.04 & \bf218.79 & \bf  0.16 & \bf  0.21 &  60.51 &  78.83 &  88.97 \\ 
%   &  & MMC & 168.66 &   0.13 &   0.18 & \bf 68.24 & \bf 84.39 &  93.19 & \bf165.65 & \bf  0.13 & \bf  0.18 &  69.42 &  84.80 &  93.83 \\ 
%   &  & TMC & 190.81 &   0.14 &   0.20 & \bf 63.77 &  82.58 &  92.13 & \bf187.53 & \bf  0.14 & \bf  0.19 &  64.04 & \bf 82.53 &  92.23 \\ 
%  RW2 & No cut-off & MC & 220.19 &   0.16 &   0.21 &  60.55 &  78.14 &  88.69 & 219.09 &   0.16 &   0.21 &  60.45 &  78.49 &  88.68 \\ 
%   &  & MMC & 167.84 &   0.13 &   0.18 &  68.34 &  84.51 &  93.20 & \bf164.16 & \bf  0.13 & \bf  0.18 &  69.59 &  85.14 & \bf 94.01 \\ 
%   &  & TMC & 188.93 &   0.14 &   0.19 &  63.64 &  82.42 &  91.99 & \bf184.27 & \bf  0.14 & \bf  0.19 &  64.73 &  82.86 & \bf 92.25 \\ 
%   & Paediatric cut-off & MC & 221.05 &   0.16 &   0.21 & \bf 60.19 &  78.27 &  88.76 & \bf218.97 & \bf  0.16 & \bf  0.21 &  60.47 & \bf 78.59 & \bf 88.78 \\ 
%   &  & MMC & 168.58 &   0.13 &   0.18 & \bf 68.33 & \bf 84.33 &  92.93 & 165.97 &   0.13 &   0.18 &  69.13 &  84.60 &  93.63 \\ 
%   &  & TMC & 191.49 &   0.14 &   0.20 & \bf 63.23 & \bf 81.74 &  91.71 & 187.82 &   0.14 &   0.19 &  63.78 &  82.34 &  92.00 \\ 
%   \hline 
%   \end{tabular} 
%   \caption{Results of the posterior predictive checking in total 
%              male circumcision (MC), medical male circumcision (MMC) and 
%              traditional male circumcision (TMC) from fitting the 12 candidate 
%              models and taking the median value across all Non-VMMC countries. Combinations include 
%              (i) Time invariant or Time variant TMC, 
%              (ii) No cut off vs. Paediatric cut-off in MMC, and 
%              (iii) Autoregressive order 1 (AR1), Random Walk 1 (RW1) or 
%              Random Walk 2 (RW2) temporal prior. 
%              For all combinations, the within-sample continuous ranked 
%              probability scores (CRPS), mean absolute error (MAE) , 
%              root mean squared error (RMSE), and the proportion of empirical 
%              observations that fell within the 50\%, 80\%, and 95\% 
%              quantiles are shown.} 
%   \label{tab::PPC1Non-VMMC} 
% \end{table}}
%  
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
